### 2024-01-06 inst/scripts/exploreNeutralTraits.Rmd

To simplify we define $K=z$ communities, all communities of hunter gatherer , with 150 individual per community, 150 will also be the Fission Threshold (ie community starts at maximum pop size).
```{r initparam}
km=0
ki=z
G=2
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=ki,km=km,n=20),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
```

@@

```{r finaldistrib}
knitr::kable(aggregate(quickV$population[,traitsid],by=list(quickV$population[,"community"]),FUN=getRatio))

@@

rhodep=lapply(c(0,1),function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

@@

#sorry :D
lapply(lapply(rhodep,lapply,matmean),lapply,image,zlim=c(0,150))
```

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=500
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)
cl <- makeCluster(15,type="FORK")
rhos=c(0,.5,1)
rhodepSB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

>>>>

To simplify we define $K=z$ communities, all communities of hunter gatherer , with 150 individual per community, 150 will also be the Fission Threshold (ie community starts at maximum pop size).
```{r initparam,out.width="40%"}
km=0
ki=z
G=2
initcomus=initialiseCommunities(traits=initAdaptiveTraits(ki=ki,km=km,n=20),coordinates=random2Dgrid(K=ki+km,Gx=G),G=G,sizes=150,plot=T)
text(initcomus$coordinates[,1],initcomus$coordinates[,2],labels=1:nrow(initcomus$coordinates))
cols=c("#E41A1C","#377EB8","#4DAF4A","#984EA3")
plot(initcomus$coordinates[,1],initcomus$coordinates[,2],bg=cols,pch=21,cex=20)
text(initcomus$coordinates[,1],initcomus$coordinates[,2],labels=1:nrow(initcomus$coordinates))
```

@@

```{r finaldistrib,fig.show="hold"}
knitr::kable(aggregate(quickV$population[,traitsid],by=list(quickV$population[,"community"]),FUN=getRatio))

barplot(as.matrix(aggregate(quickV$population[,traitsid],by=list(quickV$population[,"community"]),FUN=getRatio)[,-1]),beside=T,col=cols,main="percentage of population with traits")
barplot(table(quickV$population[,"community"]),col=cols,main="community size")

@@

rhodep=lapply(c(0,.5,1),function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)

@@

#sorry :D
lapply(lapply(rhodep,lapply,matmean),lapply,image,zlim=c(0,150),xlab="comu",x=c(1,2,3,4),y=c(1,2,3,4),ylab="traits")
```

@@

```{r,eval=F}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=500
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)
cl <- makeCluster(10,type="FORK")

rhodepSB=lapply(c(0,.5,1),function(rho){
cl <- makeCluster(10,type="FORK")

rhodepSB=lapply(c(0,1),function(rho){
cl <- makeCluster(15,type="FORK")
rhos=c(0,.5,1)
rhodepSB=lapply(rhos,function(rho){
           neutraltraitsParam$post[,]=0
           neutraltraitsParam$pre[,]=0
           neutraltraitsParam$post[,"i"]=1
           #allinlaw=replicate(repli,
           allinlaw=parSapply(cl,1:repli,function(r)
                              {
                                  set.seed(as.numeric(Sys.time())+r)
                                  quickV=modelVector(K=K, m=1, b=0.2, r=0.01, rho=rho, d=0.01, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam,age.threshold=20, out=c("traitsumary","finalpop","finalcomus","popsize"),logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 150,vidfile=NULL)
                                  pop=quickV$population
                                  #aggregate(pop[,traitsid],by=list(pop[,"community"]),sum)[-1,]
                                  sapply(1:z,function(i)apply(pop[pop[,"community"]==i,traitsid],2,sum))
                              },simplify=F)
